Sardines only end-to-end atlantisom test

### 2019-06-03 SardinesOnlyatlantisom2SStest.Rmd
flagging errors, likely fishery timesteps

```{r true-catage-lf-wtage}

@@

@@

# aggregate true resn per survey design
survey_aggresnstd <- aggregateDensityData(dat = results$resn,
                                          time = unique(results$nums$time),
                                          species = species,
                                          boxes = boxall)

# aggregate true structn per survey design
survey_aggstructnstd <- aggregateDensityData(dat = results$structn,
                                             time = unique(results$nums$time),
                                             species = species,
                                             boxes = boxall)

@@

#Extract length composition data
ss_length_stdsurv <- calc_age2length(structn = ss_structnstd,
                                     resn = ss_resnstd,
                                     nums = age_comp_data,
                                     biolprm = results$biolprm, fgs = results$fgs,
                                     CVlenage = CVs$lenage, remove.zeroes=TRUE)

@@

# catch at age by area
catch_numbers <-  create_fishery_subset(dat = truth$catch,
                                         time = fish_years,
                                         species = species,
                                         boxes = boxall)

@@

catchObsNum <- sample_survey_numbers(catch_numbers, cv=cv)

@@

#Get weights
# aggregate true resn per survey or fishery subset design
catch_aggresnss <- aggregateDensityData(dat = truth$resn,
                                 time = fish_years,
                                 species = species,
                                 boxes = boxes)

# aggregate true structn per survey or fishery subsetdesign
catch_aggstructnss <- aggregateDensityData(dat = truth$structn,
                                 time = fish_years,
                                 species = species,
                                 boxes = boxes)

@@

catch_length <- calc_age2length(structn = catch_structnss,
                                 resn = catch_resnss,
                                 nums = catch_numssshigh,
                                 biolprm = results$biolprm, fgs = results$fgs,
                                 maxbin = maxbin,
                                 CVlenage = CVs$lenage, remove.zeroes=TRUE)

@@

```{r readdata}
require(r4ss)
#source("./config/sardine_config.R") this is above for illustration

@@

```{r SS-comps-formatting}

>>>>

```{r true-catage-lf-wtage, eval=FALSE}

@@

######    CHECK fish_years   ####### get in right units  #######
# fishery output timestep
fstepperyr <- if(runpar$outputstepunit=="days") 365/runpar$toutfinc

@@

# aggregate true resn per survey design
survey_aggresnstd <- aggregateDensityData(dat = truth$resn,
                                          time = survey_sample_full,
                                          species = species,
                                          boxes = boxall)

# aggregate true structn per survey design
survey_aggstructnstd <- aggregateDensityData(dat =truth$structn,
                                             time = survey_sample_full,
                                             species = species,
                                             boxes = boxall)

@@

#Extract length composition data
ss_length_stdsurv <- calc_age2length(structn = ss_structnstd,
                                     resn = ss_resnstd,
                                     nums = age_comp_data,
                                     biolprm = truth$biolprm, fgs = truth$fgs,
                                     CVlenage = CVs$lenage, remove.zeroes=TRUE)

@@

# catch at age by area
catch_numbers <-  create_fishery_subset(dat = truth$catch,
                                         #time = fish_years,
                                         time = survey_sample_full,
                                         species = species,
                                         boxes = boxall)

@@

catchObsNum <- sample_survey_numbers(dat=catch_numbers, cv=cv)

@@

#Get weights
# aggregate true resn per survey or fishery subset design
catch_aggresnss <- aggregateDensityData(dat = truth$resn,
                                 #time = fish_years,
                                 time = survey_sample_full,
                                 species = species,
                                 boxes = boxall)

# aggregate true structn per survey or fishery subsetdesign
catch_aggstructnss <- aggregateDensityData(dat = truth$structn,
                                 #time = fish_years,
                                 time = survey_sample_full,
                                 species = species,
                                 boxes = boxall)

@@

catch_length <- calc_age2length(structn = catch_structnss,
                                 resn = catch_resnss,
                                 nums = catch_numssshigh,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 maxbin = maxbin,
                                 CVlenage = CVs$lenage, remove.zeroes=TRUE)

@@

```{r readdata}
#devtools::install_github("r4ss/r4ss", dependencies = FALSE)
require(r4ss)
#source("./config/sardine_config.R") this is above for illustration

@@

```{r SS-comps-formatting, eval=FALSE}

#getting an error in here, I think it is the definition of fish_years
#Error in x[[jj]][iseq] <- vjj : replacement has length zero
